Working Notes

### 2019-02-25 Ensemble_Notes.Rmd
update

---
title: "Notes on Building a Final Ensemble Protocol"
author: "Dan Johnson"
date: "2/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: "Final Ensemble Protocol"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

### 2019-02-25 docxcommentextraction.Rmd
Web site update
update

---
title: "DOCX Comment Extraction"
author: "Dan Johnson"
date: "2/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

#Sample Working Code
```{r}
library(docxtractr)
```

>>>>

---
title: "DOCX Comment Extraction"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

@@

#Sample Working Code
```{}
library(docxtractr)
```

### 2019-02-25 litreview.Rmd
update

---
title: "Literature Review"
date: "2/21/2019"
bibliography: library.bib
biblio-style: apalike
---

@@

#Overview
This page links out to sub-pages that describe various background topics. Follow the links for details.

Description: https://adanieljohnson.github.io/default_website/pagename.html

Technical Writing Training

Text Classification Strategies

>>>>

---
title: "Literature Review"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

#Overview
This project brings together several traditionally separate fields of research:

*  General learning theories
*  Educational research specific to STEM fields
*  Writing in the disciplines, and technical writing instruction
*  Text analysis and classification

Instead of trying to weave a coherent one-page narrative of these very different fields, I have provided links out to sub-pages for each of the various background topics. Follow the links for details.

General Learning Theories Relevant to the Current Challenge:
https://adanieljohnson.github.io/default_website/pagename.html

STEM Educational Research:
https://adanieljohnson.github.io/default_website/pagename.html

Foundations of Technical Writing Training:  https://adanieljohnson.github.io/default_website/pagename.html

Text Classification 1 - Feature Selection and Engineering:  https://adanieljohnson.github.io/default_website/Text_Classifier_Models.html

Text Classification 2 - Topic categorization and modeling (https://adanieljohnson.github.io/default_website/Topic_categorization.html)

Text Classification 3 - Selecting an appropriate text classifier method (https://adanieljohnson.github.io/default_website/Choosing_classifier.html)

Text Classification 4 - Evaluating the outcomes, and improving the classifier (https://adanieljohnson.github.io/default_website/Improving_classifier.html)

### 2019-02-25 notes.rmd
update

---
title: "Working Notes"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

#Items to get help on:

##Index:
	Site map

##Background:

##Lit review:
	How to branch to Text Classification Primer, sub-pages look okay?
		Text_classifier_models	= 	Text Classification Primer
		Topic_categorization = Topic Categorization and Modeling Methods
		Choosing_classifier = Choosing a Text Classifier Method
		Classifier_comparison = Designing a Classifier Evaluation Workflow 
		Improving_classifier = Strategies for Improving Text Classifiers

##The Build:
	df
	  df

##Data Exploration:
	Help with aligning tables and keeping the NA values

##Findings:
	How to graph the different comparisons of NB values from different sources on same plot.

##Next Steps:
	Df
	  Df

##Etc.:
	Using a Bibliography in this format
	Can menus have sub-pages
	Adding automatic updates to top dates
	Moving top dates

##Check These Out:
  Upload 'devtools::install_github("WFU-TLC/analyzr")'

>>>>

---
title: "Working Notes"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```
Items to get help on:

##General/Site-Wide:
  Embedding the bibliographic items  
    Writing the bibtext  
    Embedding using [@ BaseR] method.

##Index:
*  Decide on bottom page site map strategy

##Background:
*  Need to finish these pages:  
    +  Df
    +  Df

##Lit review:  
*  Df  
    +  Df

##The Build:
*  Find out from Melissa which method/model she is using. Useful for another project.  
    +  Df

##Data Exploration:
*  Try fixing problem of aligning tables and keeping the NA values by switching from "merge" to "full_join"  
*  Try modifying the comparison of word frequencies in all comments vs. subgroups to comparison between two subsamples from full group. How do the individual subgroups compare to a random sample? Is the variation I see just noise?  
*  For N-gram analysis, how to join tables with missing values?
    +  Use full_join, not merge.

##Findings:
*  How to graph the different comparisons of NB values from different sources on same plot? 
    +  Add ggplot (data=) value.
    +  Better to combine data into one dataset though.

#Next Steps:
*  Still in draft stage
    +  Df

#Etc.:
*  Using a Bibliography in this format  
*  Adding automatic updates to top dates? 
    +  ```date: "`r format(Sys.time(), '%b %d, %Y')`" ```

*  Fix GitHub auto-upload

##Try These Out:
*  Use Mike's Metadata packager to annotate our released dataset
*  Use ```mutate(datacolumn=str_count(utterance_clean, "\\b(um|u=m)\\b"))``` to extract a string character and count. Use this to count punctuation only comments, or ID comments with questions.
